Application of Bootstrap Resampling to REXS Data

### 2014-07-30 Articles/Article_Heun_Warr_2014/EcolEcon_HeunWarr.Rnw
Updates to HeunWarr paper.

opts_chunk$set(
  # ********************************************************
  eval=FALSE,
  # ********************************************************
  # tikz allows LaTeX code in graphical output. 
  # E.g., "$y$" for a variable name in the legend for a graph.  
  # dev='tikz',
  tidy=FALSE,
  comment=NA,
  # Tells whether to cache output from chunks are saved. Cacheing saves time. 
  # However, references to LaTeX tables DO NOT WORK if cacheing is turned on.
  cache=FALSE,
  warning=FALSE,  #Tells whether to show warnings in the output.
  # Turns off messages for all chunks. 
  # Set TRUE on an individual chunk to see it.
  message=FALSE, 
  # Tells whether to echo code for all chunks. 
  # Set TRUE on an individual chunk to see its code.
  echo=FALSE     
)
@

@@

<<CES_lambda_gamma_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with exergy ($x$).", eval=TRUE>>=
cesCoeffsData <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
                                                                     "(iK + iL) + (iX)", 
                                                                     "(iL + iX) + (iK)", 
                                                                     "(iX + iK) + (iL)"))
standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
    labs(x=expression(gamma), y=expression(lambda))
@

<<CES_sigma1_delta1_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with exergy ($x$).", eval=TRUE>>=
standardScatterPlot(data=cesCoeffsData, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta[1]), y=expression(sigma[1]))
@

<<CES_sigma_delta_graph_X, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using exergy ($x$).">>=
standardScatterPlot(data=subset(cesCoeffsData, nestStrParen != "(iK + iL) + ()"),
                    mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta), y=expression(sigma))
@

@@

<<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
standardTriPlot(data=cesCoeffsData, facet_formula=country~nestStrParen)
@

@@

<<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models.">>=
cesFittedData <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
                                                                     "(iK + iL) + (iQ)", 
                                                                     "(iL + iQ) + (iK)", 
                                                                     "(iQ + iK) + (iL)"))
spaghettiPlot(data=cesFittedData, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@

<<CES_lambda_gamma_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with useful work ($u$).", eval=TRUE>>=
cesCoeffsData <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
                                                                     "(iK + iL) + (iU)", 
                                                                     "(iL + iU) + (iK)", 
                                                                     "(iU + iK) + (iL)"))
standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
    labs(x=expression(gamma), y=expression(lambda))
@

<<CES_sigma1_delta1_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with useful work ($u$).">>=
standardScatterPlot(data=cesCoeffsData, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta[1]), y=expression(sigma[1]))
@

<<CES_sigma_delta_graph_U, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with useful work ($u$).">>=
standardScatterPlot(data=subset(cesCoeffsData, nestStrParen != "(iK + iL) + ()"),
                    mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta), y=expression(sigma))
@

Figure~\ref{fig:CES_Spaghetti_Graph_CN} shows details of the resample fits for China with the (kl)e nesting.
Again, historical data are shown as a black line. 
The fit to historical data is shown as a white line.
The gray band encompasses 95\% of the fits to resampled data.

<<CES_Spaghetti_Graph_CN, fig.pos="H", fig.align='center', fig.width=maxWidth, fig.height=maxHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
spaghettiPlot(data=subset(cesFittedData, Country=="CN" & nestStrParen=="(iK + iL) + (iQ)"), level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
@

@@

\twocolumn{}
<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
linexCoeffsData <- filter(coeffs_df, model=="linex", energy=="iQ")
standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
    labs(x=expression(a[0]), y=expression(c[t])) +
     scale_x_continuous(limits=c(-1, 2), breaks=c(-1, 0, 1.0, 2.0)) +
     scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
@

<<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
linexFittedData <- filter(fitted_df, model=="linex", energy=="iQ")
spaghettiPlot(data=linexFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@
\onecolumn{}

>>>>

opts_chunk$set(
  # ********************************************************
  eval=TRUE,
  # ********************************************************
  # tikz allows LaTeX code in graphical output. 
  # E.g., "$y$" for a variable name in the legend for a graph.  
  # dev='tikz',
  tidy=FALSE,
  comment=NA,
  # Tells whether to cache output from chunks are saved. Cacheing saves time. 
  # However, references to LaTeX tables DO NOT WORK if cacheing is turned on.
  cache=FALSE,
  warning=FALSE,  #Tells whether to show warnings in the output.
  # Turns off messages for all chunks. 
  # Set TRUE on an individual chunk to see it.
  message=FALSE, 
  # Tells whether to echo code for all chunks. 
  # Set TRUE on an individual chunk to see its code.
  echo=FALSE     
)
@

@@

<<CES_lambda_gamma_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with exergy ($x$).">>=
cesCoeffsDataX <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
                                                                      "(iK + iL) + (iX)", 
                                                                      "(iL + iX) + (iK)", 
                                                                      "(iX + iK) + (iL)"))
standardScatterPlot(data=cesCoeffsDataX, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
    labs(x=expression(gamma), y=expression(lambda))
@

<<CES_sigma1_delta1_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with exergy ($x$).">>=
standardScatterPlot(data=cesCoeffsDataX, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta[1]), y=expression(sigma[1]))
@

<<CES_sigma_delta_graph_X, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using exergy ($x$).">>=
standardScatterPlot(data=subset(cesCoeffsDataX, nestStrParen != "(iK + iL) + ()"),
                    mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta), y=expression(sigma))
@

@@

<<CES_ternary_graphX, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with exergy ($x$).">>=
standardTriPlot(data=cesCoeffsDataX, facet_formula=country~nestStrParen)
@

@@

<<CES_Spaghetti_Graph_X, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with exergy ($x$).">>=
cesFittedDataX <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
                                                                      "(iK + iL) + (iX)", 
                                                                      "(iL + iX) + (iK)", 
                                                                      "(iX + iK) + (iL)"))
spaghettiPlot(data=cesFittedDataX, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1900=1 or 1950=1)")
@

<<CES_lambda_gamma_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with useful work ($u$).">>=
cesCoeffsDataU <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
                                                                      "(iK + iL) + (iU)", 
                                                                      "(iL + iU) + (iK)", 
                                                                      "(iU + iK) + (iL)"))
standardScatterPlot(data=cesCoeffsDataU, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
    labs(x=expression(gamma), y=expression(lambda))
@

<<CES_sigma1_delta1_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with useful work ($u$).">>=
standardScatterPlot(data=cesCoeffsDataU, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta[1]), y=expression(sigma[1]))
@

<<CES_sigma_delta_graph_U, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with useful work ($u$).">>=
standardScatterPlot(data=subset(cesCoeffsDataU, nestStrParen != "(iK + iL) + ()"),
                    mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta), y=expression(sigma))
@

<<CES_Spaghetti_Graph_U, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with useful work ($u$).">>=
cesFittedDataU <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
                                                                      "(iK + iL) + (iU)", 
                                                                      "(iL + iU) + (iK)", 
                                                                      "(iU + iK) + (iL)"))
spaghettiPlot(data=cesFittedDataU, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1900=1 or 1950=1)")
@

@@

<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
linexCoeffsData <- filter(coeffs_df, model=="linex", energy %in% c("iX", "iU"))
standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
    labs(x=expression(a[0]), y=expression(c[t])) +
     scale_x_continuous(limits=c(-1, 2), breaks=c(-1, 0, 1.0, 2.0)) +
     scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
@

<<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
linexFittedData <- filter(fitted_df, model=="linex", energy %in% c("iX", "iU"))
spaghettiPlot(data=linexFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1900=1 or 1950=1)")
@
